Denotational Semantics for SSA with Weak Memory Operations

### 2023-10-11 pldi24/paper.tex
Work on structural judgements, stubs

@@

\begin{figure}
  \TODO{this}
  \caption{Typing rules for \isotopessa substitutions}
  \Description{Typing rules for isotope-SSA substitutions}
  \label{fig:ssa-block-typing}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \TODO{this}
  \end{center}
  \caption{Semantics for \isotopessa}
  \Description{Semantics for isotope-SSA}
  \label{fig:ssa-semantics}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \TODO{this}
  \end{center}
  \caption{Grammar for \isotopessa expressions with holes}
  \Description{Grammar for isotope-SSA expressions with holes}
  \label{fig:ssa-semantics}
\end{figure}

>>>>

% Denotational semantics
\newcommand{\dnt}[1]{\llbracket{#1}\rrbracket}
\newcommand{\ednt}[1]{\left\llbracket{#1}\right\rrbracket}
\newcommand{\upg}[1]{{#1}^\uparrow}

@@

\begin{figure}
  \TODO{this}
  \caption{Typing rules for \isotopessa substitutions}
  \Description{Typing rules for isotope-SSA substitutions}
  \label{fig:ssa-subst-typing}
\end{figure}

@@

\begin{figure}
  \begin{gather*}
    \boxed{\dnt{A}}: |\mc{C}_1| \\
    \dnt{X} = \ms{base}(X) 
      \text{ where } 
      \dnt{\mb{1}} = \mb{1}, 
      \dnt{\mb{2}} = \mb{2}
    \qquad \dnt{A \otimes B} = \dnt{A} \otimes \dnt{B} \\
    \boxed{\dnt{\Gamma}}: |\mc{C}_1| \\
    \dnt{\cdot} = \mb{1} \qquad 
    \dnt{\Gamma, \thyp{x}{A}{q}} = \dnt{\Gamma} \otimes \dnt{A} \\
    \boxed{\dnt{\ms{L}}}: |\mc{C}_0| \\
    \dnt{\cdot} = \mb{0} \qquad
    \dnt{\ms{L}, \llhyp{\ell}{\Gamma}{A}} = 
      \dnt{\ms{L}} + \dnt{\Gamma} \otimes \dnt{A}
  \end{gather*}
  \caption{Semantics for \isotopessa types and contexts}
  \Description{Semantics for isotope-SSA types and contexts}
  \label{fig:ssa-type-semantics}
\end{figure}

\begin{figure}
  \begin{gather*}
    \boxed{\dnt{\tlin{A}{\taff}}: \mc{C}_1(\dnt{A}, \mb{1})} \\
    \dnt{\tlin{X}{\taff}} = \ms{drop}(X) \qquad
    \dnt{\tlin{A \otimes B}{\taff}} 
      = \dnt{\tlin{A}{\taff}} \otimes \dnt{\tlin{B}{\taff}}
      ; \lambda \\
    \boxed{\dnt{\tlin{A}{\trel}}}
      : \mc{C}_1(\dnt{A}, \dnt{A} \otimes \dnt{A}) \\
    \dnt{\tlin{X}{\trel}} = \ms{split}(X) \qquad
    \dnt{\tlin{A \otimes B}{\trel}} = 
      \dnt{\tlin{A}{\trel}} \otimes \dnt{\tlin{B}{\trel}}
      ;\alpha;\dnt{A} \otimes \sigma \otimes \dnt{B};\alpha \\
    \boxed{\dnt{\csplits{\Gamma}{\Delta}{\Xi}}}
      : \mc{C}_1(\dnt{\Gamma}, \dnt{\Delta} \otimes \dnt{\Xi}) \\
    \dnt{\csplits{\cdot}{\cdot}{\cdot}} = \lambda^{-1} \qquad
    \dnt{\csplits
      {\Gamma, \thyp{x}{A}{q}}
      {\Delta, \thyp{x}{A}{q}}
      {\Xi}} 
      = \dnt{\csplits{\Gamma}{\Delta}{\Xi}} \otimes \dnt{A};\alpha;\dnt{\Delta} \otimes \sigma;\alpha \\
    \dnt{\csplits
      {\Gamma, \thyp{x}{A}{q}}
      {\Delta}
      {\Xi, \thyp{x}{A}{q}}} 
      = \dnt{\csplits{\Gamma}{\Delta}{\Xi}} \otimes \dnt{A};\alpha \\
    \dnt{\csplits
      {\Gamma, \thyp{x}{A}{q}}
      {\Delta}
      {\Xi, \thyp{x}{A}{q}}} \
      = \dnt{\Gamma} \otimes \dnt{\tlin{A}{\trel}};
        \alpha;
        \dnt{\Delta} \otimes \sigma \otimes \dnt{A};
        \alpha \\
    \dnt{\csplits
      {\Gamma, \thyp{x}{A}{q}}
      {\Delta}
      {\Xi}}
      = \dnt{\csplits{\Gamma}{\Delta}{\Xi}}
        \otimes \dnt{\tlin{A}{\taff}}
      ; \rho \\
    \boxed{\dnt{\cwk{\Gamma}{\Delta}}
      : \mc{C}_1(\dnt{\Gamma}, \dnt{\Delta})} \\
      = \dnt{\csplits{\Gamma}{\Delta}{\cdot}};\rho \\
    \boxed{\dnt{\lwk{\ms{L}}{\ms{K}}}
      : \mc{C}_0(\dnt{\ms{L}}, \dnt{\ms{K}})} \\
      \dnt{\lwk{\cdot}{\cdot}} = \ms{id} \qquad
      \dnt{\lwk
        {\ms{L}, \llhyp{\ell}{\Gamma}{A}}
        {\ms{K}, \llhyp{\ell}{\Gamma}{A}}}
        = \dnt{\lwk{\ms{L}}{\ms{K}}} + \dnt{\Gamma} \otimes \dnt{A} \\
      \dnt{\lwk{\ms{L}}{\ms{K}, \llhyp{\ell}{\Gamma}{A}}}
        = \dnt{\lwk{\ms{L}}{\ms{K}}};\rho_+^{-1}
        ; \dnt{\ms{K}} \oplus 0_{\dnt{\Gamma} \otimes \dnt{A}}
  \end{gather*}
  \caption{Semantics for \isotopessa structural judgements}
  \Description{Semantics for isotope-SSA structural judgements}
  \label{fig:ssa-structural-semantics}
\end{figure}

\begin{figure}
  \TODO{this}
  \caption{Semantics for \isotopessa terms}
  \Description{Semantics for isotope-SSA terms}
  \label{fig:ssa-structural-terms}
\end{figure}

\begin{figure}
  \TODO{this}
  \caption{Semantics for \isotopessa blocks}
  \Description{Semantics for isotope-SSA blocks}
  \label{fig:ssa-structural-blocks}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \TODO{this}
  \end{center}
  \caption{Grammar for \isotopessa terms and blocks with holes}
  \Description{Grammar for isotope-SSA terms and blocks with holes}
  \label{fig:ssa-semantics}
\end{figure}
